Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-27 EconGrowth.Rnw
Now generating a lattice graph for factors of production for each country.

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=6,
  fig.height=4,
#  out.width=".45\\textwidth",
#  out.height=".38\\textwidth",
  comment=NA)

@@

<<creategraph>>=

createCountryInputGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graph <- xyplot(iGDP+iQ+iX+iCapStk+iLabor ~ iYear, data=dataTable,
                  type="l",
                  scales=list(cex=1.0, tck=-0.5),
                  ylab="Indexed (1980=1)",
                  auto.key=list(columns=1, x=0.0, y=0.98))
  return(graph)
}

createCountryInputGraph("US")
lapply(countries, createCountryInputGraph)

>>>>

<<setup, include=FALSE>>=
require(knitr)
require(lattice)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=FALSE)
opts_chunk$set(
  tidy=FALSE,
  fig.width=6.5,
  fig.height=4.5,
#  out.width=".45\\textwidth",
#  out.height=".38\\textwidth",
  comment=NA)

@@

<<graphs>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.92),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

createGDPComparisonGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1) #line widths
  colors <- c("black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iGDP ~ Year, data=dataTable,
                  key=list(text=list(c("GDP")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}

# createGDPComparisonGraph <- function(countryName){
#   dataTable <- loadData(countryName)
#   graphType <- "l"
#   colors <- c("black", "black", "black", "black") #line and point colors
#   lineWidths <- c(1, 1, 1, 1) #line widths
#   lineTypes <- c(1, 5, 2, 4) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
#   lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
#   pointSpec <- list(col=colors)
#   graph <- xyplot(iGDP ~ iYear, data=dataTable,
#                   key=list(text=list(c("GDP")),
#                            type=graphType,
#                            lines=lineSpec,
#                            columns=1, x=0.0, y=0.98),
#                   type=graphType,
#                   par.settings = list(superpose.line = lineSpec),
# #                                      superpose.symbol = pointSpec),
#                   scales=list(cex=1.0, #controls text size on scales
#                               tck=-0.5), #controls tick mark length
#                   ylab="Indexed (1980=1)")
#   return(graph)
# 
#                     
# }

createFactorsLatticeGraph("All")

#createGDPComparisonGraph("US")

#createCountryFactorsGraph("US")
#lapply(countries, createCountryFactorsGraph)
